InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-30 paper.tex
Added two more image generative models

>>>>

Another image generative model is the \textbf{midjourney} \cite{midjourney}. This model was created by an independent research lab with the same name. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists and it uses modern deep learning methods to create high-quality images.

\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding. Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation. More information can be found either on their website \cite{imagen} or in their paper \cite{saharia2022photorealistic}.
